### 2016-10-31 oldmort.Rnw
fixing...

<<readtab>>=
## We want to add hisclass at 40 (hc40) and hisclass at 60 (hc60), so as a shortcut
## we start over with vb in the creation of the 'new vbTab':
##load("data/vbTab.rda") 
load("data/vb.rda")
vb <- vb[order(vb$id, vb$age), ]
vb$exposure <- with(vb, exit - enter)
first <- function(x) x[1]
hisclass40 <- with(vb, tapply(hisclass, id, first))
indx <- match(vb$id, names(hisclass40))
vb$hisclass40 <- hisclass40[indx]
##
vb$hisclass60 <- 0
hisclass60 <- with(vb[vb$age > 59, ], tapply(hisclass, id, first))
indx <- match(vb$id, names(hisclass60))
vb$hisclass60 <- hisclass60[indx]
komp <- is.na(vb$hisclass60)
vb$hisclass60[komp] <- vb$hisclass40[komp]
vb$hisclass40 <- factor(vb$hisclass40, labels = c("1+2", "3+4", "5", "6+7"))
vb$hisclass60 <- factor(vb$hisclass60, labels = c("1+2", "3+4", "5", "6+7"))
## Now to the creation of vbTab:
vbTab <- aggregate(vb[, c("event", "exposure")],
                   vb[, c("sex", "age", "period", "cohort", "urban",
                          "civst", "hisclass40", "hisclass60")],
                   FUN = sum)
vbTab$age <- factor(vbTab$age)
@

@@

<<causes41>>=
load("data/vb.rda")
vb <- cal.window(vb, c(1961, 2001))
x <- substr(vb$ULORSAK, 1, 2)
vb$event <- vb$event & (!is.na(x) & (x == "19"))
vb$exposure <- with(vb, exit - enter)
vb$cohort <- factor(vb$cohort)
vb$period <- factor(vb$period)
vbTab <- aggregate(vb[, c("event", "exposure")], 
                   vb[, c("sex", "age", "period", "cohort", 
                          "urban", "civst", "hisclass")], 
                   FUN = sum)
vbTab$hisclass <- factor(vbTab$hisclass)
vbTab$age <- factor(vbTab$age)
@

>>>>

<<readtab>>=
load("data/vbTab.rda") 
load("data/vb.rda")
@

@@

<<causes41>>=
load("data/vb.rda")
##vb <- cal.window(vb, c(1961, 2001))
##x <- substr(vb$ULORSAK, 1, 2)
vb$event <- vb$event & vb$heart
vb$exposure <- with(vb, exit - enter)
vb$cohort <- factor(vb$cohort)
vb$period <- factor(vb$period)
vbTab <- aggregate(vb[, c("event", "exposure")], 
                   vb[, c("sex", "age", "period", "cohort", 
                          "urban", "civst", "hisclass")], 
                   FUN = sum)
vbTab$hisclass <- factor(vbTab$hisclass)
vbTab$age <- factor(vbTab$age)
@
